### 2008-09-25 doc/client/client_technical.tex
Fix description to match the figure

\begin{enumerate}
\item{The {\TargetGenerator} takes three arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second and third arguments contain lists of strings. The first list
  contains individually selected and rejected computing services,
  while the second list contains individually selected and rejected
  index servers. Rejected servers and services are identified by that
  its name is prefixed by a minus sign in the lists. The name of the
  servers and services should be given either in the form of an alias
  defined in the {\UserConfig} object or as the name of its grid
  flavour followed by a colon and the URL of its information contact
  endpoint.}
\item{These lists are parsed through alias resolution before being
  used to initialize the complete list of selected and rejected
  {\URL}s pointing to computing services and index servers.}
\item{An external call is received calling for targets to be
  prepared.}
\item{For each selected index server and computing service a
  {\TargetRetriever} plugin for the server's or service's grid flavour
  is loaded using the ARC loader. The {\TargetRetriever} is
  initialized with its {\URL} and the information about whether it
  represents a computing service or an index server. The call for
  targets is processed by each {\TargetRetriever} in parallel.}
\item{A {\TargetRetriever} representing an index server first tries to
  register at the index server store kept by the {\TargetGenerator}.
  If allowed to register, the index server is queried and the query
  result processed. The {\TargetGenerator} will not allow
  registrations from index servers present in its list of rejected
  index servers or from servers that have already registered
  once. Index servers often register at more than one index server,
  thus different {\TargetRetriever}s may discover the same server.}
\item{If while processing the query result the {\TargetRetriever}
  finds an other registered index server or a registered computing
  service it creates a new {\TargetRetriever} for the found server or
  service and forwards the call for targets to the new
  {\TargetRetriever}.}
\item{A {\TargetGenerator} representing a computing service first
  tries to register at the service store kept by the
  {\TargetGenerator}. If allowed to register, the computing server is
  queried and the query result processed. The {\TargetGenerator} will
  not allow registrations from computing services present in its list
  of rejected computing services or from service that have already
  registered once. Computing services often register at more than one
  index server, thus different {\TargetRetriever}s may discover the
  same service.}
\item{When processing the query result the {\TargetRetriever} will
  create an {\ExecutionTarget} for each queue found on the computing
  service and collect all possible information about them. It will
  then store the {\ExecutionTarget} in the found targets store kept
  by the {\TargetGenerator} for later usage (e.g.\ status printing or
  job submission).}
\end{enumerate}

>>>>

\begin{enumerate}
\item{The {\TargetGenerator} takes three arguments as input. The first
  argument is a reference to a {\UserConfig} object containing a
  representation of the contents of the user's configuration file. The
  second and third arguments contain lists of strings. The first list
  contains individually selected and rejected computing services,
  while the second list contains individually selected and rejected
  index servers. Rejected servers and services are identified by that
  its name is prefixed by a minus sign in the lists. The name of the
  servers and services should be given either in the form of an alias
  defined in the {\UserConfig} object or as the name of its grid
  flavour followed by a colon and the URL of its information contact
  endpoint.}
\item{These lists are parsed through alias resolution before being
  used to initialize the complete list of selected and rejected
  {\URL}s pointing to computing services and index servers.}
\item{For each selected index server and computing service a
  {\TargetRetriever} plugin for the server's or service's grid flavour
  is loaded using the ARC loader. The {\TargetRetriever} is
  initialized with its {\URL} and the information about whether it
  represents a computing service or an index server.}
\item{An external call is received calling for targets to be
  prepared. The call for targets is processed by each
  {\TargetRetriever} in parallel.}
\item{A {\TargetRetriever} representing an index server first tries to
  register at the index server store kept by the {\TargetGenerator}.
  If allowed to register, the index server is queried and the query
  result processed. The {\TargetGenerator} will not allow
  registrations from index servers present in its list of rejected
  index servers or from servers that have already registered
  once. Index servers often register at more than one index server,
  thus different {\TargetRetriever}s may discover the same server.}
\item{If while processing the query result the {\TargetRetriever}
  finds an other registered index server or a registered computing
  service it creates a new {\TargetRetriever} for the found server or
  service and forwards the call for targets to the new
  {\TargetRetriever}.}
\item{A {\TargetGenerator} representing a computing service first
  tries to register at the service store kept by the
  {\TargetGenerator}. If allowed to register, the computing server is
  queried and the query result processed. The {\TargetGenerator} will
  not allow registrations from computing services present in its list
  of rejected computing services or from service that have already
  registered once. Computing services often register at more than one
  index server, thus different {\TargetRetriever}s may discover the
  same service.}
\item{When processing the query result the {\TargetRetriever} will
  create an {\ExecutionTarget} for each queue found on the computing
  service and collect all possible information about them. It will
  then store the {\ExecutionTarget} in the found targets store kept
  by the {\TargetGenerator} for later usage (e.g.\ status printing or
  job submission).}
\end{enumerate}
